Untangling the link between traits, size and growth rate in plants

### 2015-02-06 fitting.Rmd
Update from maker -> remake

m <- maker::maker()
data <- m$make("BCI_species_data")
head(data)
```

@@

```{r, echo=TRUE, results="hide"}
data <- m$get("BCI_species_data") %>%
  mutate(dbh=at) %>%
  filter(!is.na(lma*rho*hmat*dbh*dbasal_diam_dt), dbh %in% c(0.01), hmat > 10) %>%
  select(dbh, lma, rho, dbasal_diam_dt)
```

>>>>

data <- remake::make("BCI_species_data")
head(data)
```

@@

```{r, echo=TRUE, results="hide"}
data <- remake::make("BCI_species_data") %>%
  mutate(dbh=at) %>%
  filter(!is.na(lma*rho*hmat*dbh*dbasal_diam_dt), dbh %in% c(0.01), hmat > 10) %>%
  select(dbh, lma, rho, dbasal_diam_dt)
```
